Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-15 paper.tex
edited new conclusion paragraph, removed note

\todo{kyle double check that this paragraph reads well}
\revise{Significant speedups in shallow SIMD-vectorized execution over a parallel OpenMP code were demonstrated for evaluations of the chemical kinetic source-term and sparse\slash dense Jacobian: up to \SI{4.09}{$\times$}, \SI{9.44}{$\times$}, and \SI{4.23}{$\times$}, respectively, on an \avx/-capable CPU.}
\revise{Sparse Jacobian evaluation was slower than dense evaluation on all CPU\slash GPU platforms due to indirect lookup requirements in array indexing, however the shallow-vectorized OpenCL code was less adversely affected than OpenMP.}
\revise{Further, analytical Jacobian evaluation was significantly faster than a first-order finite-difference based approach on all platforms.}
\revise{Finally, the performance of dense analytical-Jacobian evaluation in this new version of \texttt{pyJac} was compared to the previous version~\cite{pyjac16}; OpenMP evaluation on the CPU was moderately slower for the smallest chemical model (e.g., \SI{1.79}{$\times$} on the \avx/ CPU), but significantly faster (up to \SI{10.19}{$\times$}) for the larger models, while the shallow-vectorized OpenCL code was faster than the previous version over all chemical models, reaching speedups of \SI{19.56}{$\times$}.}

>>>>

\revise{We demonstrated significant speedups in shallow SIMD-vectorized execution over a parallel OpenMP code for evaluating the chemical-kinetic source terms and sparse\slash dense Jacobian: up to \SI{4.09}{$\times$}, \SI{9.44}{$\times$}, and \SI{4.23}{$\times$}, respectively, on an \avx/-capable CPU.
Sparse Jacobians evaluate more slowly than dense Jacobians on all CPU\slash GPU platforms due to indirect lookup requirements in array indexing, but this adversely affects the shallow-vectorized OpenCL code less than OpenMP.
Further, analytical Jacobians evaluate significantly faster than a first-order finite-difference-based approach on all platforms.
Finally, we compared the performance of evaluating dense, analytical Jacobians in this new version of \texttt{pyJac} with the previous version~\cite{pyjac16}.
The OpenMP version evaluates moderately slower on the CPU for the smallest chemical model (e.g., \SI{1.79}{$\times$} on the \avx/ CPU), but significantly faster for the larger models---up to \SI{10.19}{$\times$}.
The shallow-vectorized OpenCL code runs faster than the previous version over all chemical models, reaching speedups of \SI{19.56}{$\times$}.}
